### 2017-04-05 paper/evaluation.tex
minor changes to first par. RQ3

\begin{itemize}
    \item \textbf{\RQD}
\end{itemize}

To answer \numRQD{}, we considered \numProjectsPar{} subjects that we
tested and confirmed parallelization activated by default (see
Section~\ref{sec:rqC-1}). To measure the overall speedup obtained from
parallel execution, we compared the elapsed time from the default
execution (parallelization enabled) and the elapsed time from the
sequential execution.  For each project, we modified the existing
configurations to disable the parallel test execution. In addition, we
verified that both executions produce the same outcome to eliminate
noise from failing tests.
To compute the speedup, we divide the time obtained in the sequential
execution by the time obtained from the default execution.  For
instance, if a project runs the tests sequentially in $10m$ and the
same execution runs in $5m$ with parallelization enabled (default
execution), the speedup is two.

@@

>>>>

\begin{itemize}
    \item \numRQD{}. \textbf{\RQD}
\end{itemize}

To answer \numRQD{}, we considered all \numProjectsPar{} subjects from
our benchmark that use parallelization by default in Maven to run
tests.  Section~\ref{sec:rqC-1} describes in detail our methodology to
identify these subjects. For each project, the speedup (or slowdown)
corresponds to the ratio between the elapsed time of a sequential
execution and the elapsed time of a corresponding parallel execution,
obtained as described in the script from
Figure~\ref{fig:mvn-execution}.  As usual, a ratio above 1x denotes
speedup and a ratio below 1x denotes slowdown.

For each project, we modified the existing configurations to disable
the parallel test execution. In addition, we verified that both
executions produce the same outcome to eliminate noise from failing
tests.  To compute the speedup, we divide the time obtained in the
sequential execution by the time obtained from the default execution.
For instance, if a project runs the tests sequentially in $10m$ and
the same execution runs in $5m$ with parallelization enabled (default
execution), the speedup is two.

@@

\begin{itemize}
    \item \textbf{\RQF{}}
\end{itemize}

\Fix{WIP}

\begin{center}
\fbox{
\begin{minipage}{8cm}
\textit{Answering \numRQF{}:~\emph{\Jbc{summarize findings...}}}
\end{minipage}
}
\end{center}
